\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-09-27 chapters/wcble.tex
Accuracy results

\todo{figure}

\subsection{Latency estimation}

We compared our proposed \ac{wcble} algorithm to \ac{cble} on a latency
estimation task using the pearson correlation coefficient $\rho$\todo{equation} at different
jitter and \ac{snr} levels.
For both \ac{cble} and \ac{wcble}, target latencies where extracted in a
10-fold cross-validation scheme using the robust median latency method after
fitting the model.
\Ac{wcble}'s maximum iteration number was set to 64.
Results are presented in Figure~\ref{fig:wcble/results/latency}.

\begin{figure}
  \includegraphics[width=\textwidth]{figures/wcble/fig_latency.pdf}
  \caption{align results}
  \label{fig:wcble/results/latency}
\end{figure}
\todo{invert x axis}
\todo{caption}
\todo{properly label axes}
\todo{discuss results}

\subsection{Classification}
Similar to the previous experiment, classification accuracy between target and
non-target epochs is assessed.

@@

>>>>

\subsection{Latency estimation}
\todo{refer to figure}
We compared our proposed \ac{wcble} algorithm to \ac{cble} on a latency
estimation task using the pearson correlation coefficient $\rho$\todo{equation} at different
jitter and \ac{snr} levels.
For both \ac{cble} and \ac{wcble}, target latencies where extracted in a
10-fold cross-validation scheme using the robust median latency method after
fitting the model.
\Ac{wcble}'s maximum iteration number was set to 64.
Results are presented in Figure~\ref{fig:wcble/results/latency}.

\begin{figure}
  \sansmath
  \input{figures/wcble/fig_latency.pgf} \\
  \input{figures/wcble/fig_accuracy.pgf}
  \caption{align results}
  \label{fig:wcble/results/latency}
\end{figure}
\todo{invert x axis}
\todo{caption}
\todo{properly label axes}
\todo{discuss results}

As the \ac{snr} decreases, both \ac{cble} and \ac{wcble} can accurately
estimate evoked potential latencies up to a given threshold. After this
threshold, correlation between estimated and ground-truth latencies will start
decreasing.
However, we notice that this threshold occurs later for \ac{wcble} than for
\ac{cble} for all evaluated jitter levels, indicating that \ac{wcble} is more
robust in the presence of pink spatiotemporal noise.
At around -28dB, \ac{wcble} does not significantly outperform \ac{cble}
anymore and both methods get overtaken by the strong presence of noise.

\subsection{Classification}
\todo{refer to figure}
Similar to the previous experiment, classification accuracy between target and
non-target epochs is assessed.

@@

Reason that accuracy latency estimation plateaus and accuracy drops for cble,
but that both plateau for wcble, is because of the alignment
